
\begin{thebibliography}{99}
\setlength{\itemsep}{0.25em}
\setlength{\parskip}{0pt}
\setlength{\parsep}{0pt}
\subsection*{Textos}
\bibitem{millman}
J.~Millman and A.~Grabel,
``Microelectrónica,''
\emph{McGraw-Hill},
Nueva York, NY, USA, 1987.

\bibitem{herpy}
M.~Herpy,
``Analog Integrated Circuits,''
\emph{John Wiley \& Sons},
Nueva York, NY, USA, 1980.

\bibitem{frederiksen}
T.~M. Frederiksen,
``Intuitive IC Op Amps,''
\emph{National Semiconductor Corp.},
Santa Clara, CA, USA, 1984.

\bibitem{rashid}
M.~H. Rashid,
``Circuitos Microelectrónicos: Análisis y Diseño,''
\emph{Thomson Editores},
México, 2000.

\bibitem{tobey}
G.~E. Tobey, J.~G. Graeme, and L.~P. Huelsman,
``Operational Amplifiers: Design and Applications,''
\emph{McGraw-Hill},
Nueva York, NY, USA, 1971.
\subsection*{Notas Técnicas}
\bibitem{wong}
J.~Wong and A.~García,
``Precision Transducer Interfaces,''
\emph{Analog Devices},
Amplifiers Applications Guide, 1992.

\bibitem{kester}
W.~Kester, S.~Wurcer, and C.~Kitchin,
``High Impedance, Low Current Applications,''
\emph{Analog Devices},
Amplifiers Applications Guide, 1992.

\bibitem{burr_ab090}
``Op Amp Performance Análisis,''
\emph{Burr-Brown},
AB-090.

\bibitem{burr_ab075}
``Photodiode Monitoring with Operational Amplifiers,''
\emph{Burr Brown},
AB-075.

\bibitem{national_oa25}
``Stability Analisis of  Current Feedback Amplifiers,''
\emph{National Semiconductors},
OA25, May 1995.

\bibitem{intersil_an9420}
``Current Feedback Amplifiers-Theory and Applications,''
\emph{Intersil},
AN9420.1, April 1995.

\bibitem{national_oa07}
``Current Feedback  OP. Amp – Applications Circuits Guide,''
\emph{National Semiconductors},
OA 07, May 1988.

\bibitem{ti_opa684}
``OPA-684- Current Feedback Amplifiers- (Applications),''
\emph{Texas Instrument},
SBOS219A.

\bibitem{burr_ab091}
``Voltage –Feedback Amplifiers vs Current Feedback Amplifiers,''
\emph{Burr Brown},
AB-091.

\bibitem{burr_ab193}
``The Current Feedback Op-Amp a High Speed Building Block,''
\emph{Burr-Brown},
AB -193.
\bibitem{burr_ab183}
``New Ultra High –Speed Circuits Techniques with Analog ICs,''
\emph{Burr-Brown},
AB- 183.

\bibitem{burr_ab180}
``Ultra High Speed ICs,''
\emph{Burr Brown},
AB-180.

\bibitem{national_1996}
``National Linear Seminar-1996,''
\emph{National Semiconductors}.

\bibitem{dualibe}
C.~F. Dualibe,
``GMC,''
\emph{Edición Interna}.
\end{thebibliography}